Query Optimization for Dynamic Imputation

### 2017-03-01 paper/introduction.tex
paper: fix intro

% Implications
Our approach enables an exploratory analysis workflow in which the analyst can issue standard SQL queries over a data set, even if that data has missing values, and get
queries that execute between \lowxalphazero{} and \highxalphaoneexacs{} times as fast as it takes to impute all missing values and then run queries (the traditional approach). Furthermore, the results obtained with this approach
are similar in quality to those obtained with the complete imputation approach, as indicated by low Symmetric-Mean-Absolute-Percentage-Errors --- between \lowsmapealphazero{} and \highsmapealphaoneexacs{} percent --- in our empirical results
over real-world data sets (see~\Cref{sec:experiments} for details).

>>>>

% Implications
Our approach enables an exploratory analysis workflow in which the analyst can issue standard SQL queries over a data set, even if that data has missing values, and get
queries that execute between \lowxalphazero{} and \highxalphazeroexacs{} times as fast as it takes to impute all missing values and then run queries (the traditional approach). Furthermore, the results obtained with this approach
are similar in quality to those obtained with the complete imputation approach, as indicated by low Symmetric-Mean-Absolute-Percentage-Errors --- between \lowsmapealphazero{} and \highsmapealphaoneexacs{} percent --- in our empirical results
over real-world data sets (see~\Cref{sec:experiments} for details).
